---
title       : Titanic disaster 
subtitle    : Decision tree application 
author      : rydt
job         : data scientist
framework   : io2012       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## My application
This application allows to perform predictions on the survival of a person in the Titanic. The problem is taken from the kaggle competition in the knowlegde section called: *Titanic: Machine Learning from Disaster* https://www.kaggle.com/c/titanic-gettingStarted

The prediciton is made using a **decision tree** and the **rpart** library

It's easy to use:

- On the left panel, select the features to predict the survived variable 
- Click on submit
- On the right, choose a panel to get a specific view of the results (Tree, summary, CP, confusion matrix)
- Change features, click on submit and see the changes

--- .class #id 

## An example
For the features:
- Pclass (passenger class)
- Sex
- Age
- Fare (price of the ticket)
```{r, echo=FALSE}
library(rpart)

traindf<-read.csv("./data/train.csv",stringsAsFactors=FALSE)
testdf<-read.csv("./data/test.csv")

train <- traindf[c(1:691),]
test <-  traindf[c(692:891),]

# test$Survived<-NA
```

```{r, fit}
fitTree<-rpart(Survived~ Pclass + Sex + Age + Fare, data = train, method="class")
prediction <- predict(fitTree,test, type="class")

```

--- .class #id 


## Tree and Error
```{r, echo=FALSE, fig.height=10, fig.width = 10}
par(mfrow=c(1,2),oma=c(7,2,0,2))
plot(fitTree, uniform=TRUE, main="Prediction Tree ")
text(fitTree, use.n=TRUE, all=TRUE, cex=.8)

plotfit <- plotcp(fitTree) # visualize cross-validation results
```

--- .class #id 
## How well did you predict the end!!
```{r, echo=TRUE}
table(test$Survived,prediction)
```

```{r, echo=FALSE}
TN <- table(test$Survived,prediction)[1]
FN <- table(test$Survived,prediction)[2] 
FP <- table(test$Survived,prediction)[3]
TP <- table(test$Survived,prediction)[4]
```

```{r, echo=TRUE}
precision <- TP/(TP+FP)
recall <- TP/(TP+FN)
accuracy <- (TP+TN)/(TP+TN+FP+FN)
F1 <- (2*precision * recall)/(precision+recall)
```

```{r, echo=FALSE}
paste('The model has a precision of', round(precision,2),', a recall of', round(recall,2))
paste('an accuracy of', round(accuracy,2),'and an F1 score of', round(F1,2))
```

*Your turn just have fun!!!*

--- .class #id 

